CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-11-26 paper/ms.tex
structure change

@@

\subsection{\label{sec:level2} Obtain new information from the individual exposures}

After calibrate the radial velocity, we can re-generate fluxes in Apstar files by using Apvisit files. The interpolation method we use is Sinc interpolation.

>>>>

\subsection{\label{sec:level2} Obtain information from the individual exposures}

@@
